### 2017-02-02 local-capability-machine.tex
Fix a latex problem I caused.
Oops, forgot a case.

@@

   then  $\npair{((\perm',\gl'),\start,\addrend,\addr)}\in \stdvr(W)$
 \end{lemma}
 \begin{proof}
   By inspection of the definition of $\stdvr(W)$, everything follows trivially
   except the result from lemma~\ref{lem:pwl-writecond-implies-nwl}.

    If $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W)$ then $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W) \}$

  \end{enumproof}
 \end{proof}

>>>>

 \begin{lemma}[execCond implies entryCond]
   \label{lem:execCond-implies-entryCond}
   If $\npair{(\exec,\start,\addrend)} \in \execCond{}(\gl)(W)$ then
     $\npair{(\start,\addrend,\addr)} \in \entryCond{}(\gl)(W)$.
 \end{lemma}
 \begin{proof}
   \begin{enumproof}
   \item Assume: $n' < n$, $W' \future W$ where $\gl = \local \Rightarrow
     \future = \futurewk$ and $\gl = \glob \Rightarrow \future = \futurestr$
     \\
     Suffices: $\npair[n']{((\exec,\gl),\start,\addrend,\addr)} \in \stder(W')$
   \item Case $\addr \in [\start,\addrend]$: Follows from the definition of
     $\execCond{}$.
   \item Case $\addr \not\in[\start,\addrend]$: Follows by
     Lemma~\ref{lem:failed-obs-stder}.
   \end{enumproof}
 \end{proof}

@@

   then  $\npair{((\perm',\gl'),\start,\addrend,\addr)}\in \stdvr(W)$
 \end{lemma}
 \begin{proof}
   By inspection of the definition of $\stdvr(W)$, everything follows trivially
   except the following.

   \begin{enumproof}
   \item If $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W)$ then
     $\npair{(\start,\addrend)} \in \writeCond{}(\iota^\nwl,\gl)(W)$: holds
     by lemma~\ref{lem:pwl-writecond-implies-nwl}.
   \item If $\npair{(\exec,\start,\addrend)} \in \execCond{}(\gl)(W)$ then
     $\npair{(\start,\addrend,\addr)} \in \entryCond{}(\gl)(W)$.
   \end{enumproof}
 \end{proof}
